---
title: "InitialAnalysis"
author: "Efehan Danışman"
date: "11 Kasım 2018"
output: html_document
---

```{r setup, include=FALSE,eval=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(forcats)
library(scales)
library(knitr)
```

## R Markdown

We obtained electricty cuts data in Turkey between 2012 and 2018 from the Energy Transparency Platform. Data contain 51630 rows and 7 variables.

Objectives of this project is as follows:

# Learning Objectives
* Cleaning dirty data and doing text mining in order to extract insights.
* Visualizing data according to different variables.
* Visualizing geographical data over the map.

# Analysis Objectives
* Finding longest and shortest cuts and visualizing them.
* Visualizing cuts at the power plants according to city and duration.
* Finding top reasons of electricity cuts with tidy text mining.
* Analyzing cuts vis-a-vis to capacity and total power at the power plant.

```{r Getting the Data}
# Create a temporary file
tmp<-tempfile(fileext=".csv")

# Download file from repository to the temp file
download.file("https://github.com/MEF-BDA503/gpj18-first/blob/master/dataset_candidates/ArizaBakim-01012008-01012018.csv?raw=true",destfile=tmp)

```

```{r Initial Cleaning and Analysis}
# Reading data. Encoding as Latin-1 is crucial in order to see Turkish characters properly.
cuts<-read.csv(tmp, encoding= "Latin-1")

# Checking what we have as data.
str(cuts)

# Change type of time and date
cuts$Olay.Başlangıç.Tarihi <- dmy_hm(cuts$Olay.Başlangıç.Tarihi)
cuts$Olay.Bitiş.Tarihi <- dmy_hm(cuts$Olay.Bitiş.Tarihi)

# Looks like data is until beginning of the 2018 and we have between 10-12K cuts per year between 2014 and 2017.
cuts %>% group_by(year=floor_date(Olay.Başlangıç.Tarihi,"year")) %>% summarize(Olay.Başlangıç.Tarihi=n())
```

